***De novo* clustering methods out-perform reference-based methods for assigning 16S rRNA gene sequences to operational taxonomic units**

### 2015-10-08 Schloss_Cluster_PeerJ_2015.Rmd
Change title

---
title: "**Accuracy and precision of 16S rRNA gene sequence assignments to OTUs is more important than the stability of OTUs**"
author: Patrick D. Schloss* and Sarah L. Westcott
date: '`r format(Sys.Date(), format="%B %d, %Y")`'
bibliography: references.bib
output:
  pdf_document:
    includes:
      in_header: header.tex
csl: peerj.csl
fontsize: 11pt
geometry: margin=1.0in
---

## To Do:
* references
* revise
* subsample vs. sub-sample

>>>>

---
title: "***De novo* clustering methods out-perform reference-based methods for assigning 16S rRNA gene sequences to operational taxonomic units**"
author: Patrick D. Schloss* and Sarah L. Westcott
date: '`r format(Sys.Date(), format="%B %d, %Y")`'
bibliography: references.bib
output:
  pdf_document:
    includes:
      in_header: header.tex
csl: peerj.csl
fontsize: 11pt
geometry: margin=1.0in
---

## To Do:
* references
* abstract
* revise
